Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
break lines

Table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from the literature~\cite{Franklin15,maglev,converters,CTMS}. \textit{DC Motor Position} plant describes the rotary motion that coupled with wheels and cables provides translational motion. \textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension. \textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a metal ball hanged in air. \textit{Buck Converter} plant represents a power converter that steps down voltage from the supply to the load while stepping up current. \textit{Boost Converter} plant also represents a power converter, but here it steps up voltage from the supply to the load while stepping down current. \textit{Buck-boost Converter} plant represents the model of a converter that has an output voltage magnitude, which is either greater than or less than the input voltage magnitude. \textit{Automotive Cruise System} plant describes a system's model that represents the speed of a motor vehicle. \textcolor{red}{\textit{DC Motor Rate} plant describes...}. \textit{Helicopter Longitudinal Motion} plant provides the longitudinal motion model of a helicopter. \textit{Inverted Pendulum} plant describes the model of a pendulum with its center of mass above its pivot point. \textit{Magnetic Suspension} plant provides the model for which a given object is suspended via a magnetic field.

All benchmarks were discretized with different sample times using the approach described in the Appendix~\ref{sec:appendix}. All experiments were performed considering $x_{i}^{-}=-1$ and $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.

>>>>

Table~\ref{table:State-space benchmarks} summarizes all benchmarks extracted 
from the control system literature~\cite{Franklin15,maglev,converters,CTMS}. 
\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively, that coupled with wheels and cables provides 
translational motion. 
\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
control based on the pitch dimension. 
\textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a 
metal ball hanged in air. 
\textit{Buck Converter} plant represents a power converter model that steps down 
voltage from the supply to the load while stepping up current. 
\textit{Boost Converter} plant also represents a power converter model, but here 
it steps up voltage from the supply to the load while stepping down current. 
\textit{Buck-boost Converter} plant represents a converter model that has an output 
voltage magnitude, which is either greater than or less than the input voltage magnitude. 
\textit{Automotive Cruise System} plant describes the model that represents 
the speed of a motor vehicle. 
\textit{Helicopter Longitudinal Motion} plant provides the 
longitudinal motion model of a helicopter. 
\textit{Inverted Pendulum} plant describes the model of a pendulum 
with its center of mass above its pivot point. 
\textit{Magnetic Suspension} plant provides the model for which 
a given object is suspended via a magnetic field. 
\textit{Magnetized Pointer} plant describes a model rotated through interaction 
with magnetic fields, which is typically employed in analog gauges and indicators.

All benchmarks were discretized with different sample times using 
the approach described in the Appendix~\ref{sec:appendix}. 
All experiments were performed considering $x_{i}^{-}=-1$ and 
$x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
